\documentclass[a4paper,10pt]{article}

\usepackage{fullpage}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{stmaryrd}
\usepackage{mathtools}
\usepackage{epsfig}
\usepackage{hyperref}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{colortbl}
\usepackage{multirow}% http://ctan.org/pkg/multirow
\usepackage{hhline}%
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[inline]{enumitem}
\usepackage{xcolor}
\usepackage{array}
\usepackage{float}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{cleveref}
\usepackage{url}
\usepackage{listings}
\usepackage[
	lambda,advantage,adversary,probability,
	sets,notions,asymptotics,keys,
	operators,ff,primitives
]{cryptocode}
\usepackage{tcolorbox}
\usepackage{todonotes}


\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstset{
	backgroundcolor=\color{backcolour},   
  commentstyle=\color{codegreen},
  keywordstyle=\color{magenta},
  numberstyle=\tiny\color{codegray},
  stringstyle=\color{codepurple},
  basicstyle=\ttfamily\footnotesize,
  breakatwhitespace=false,         
  breaklines=true,                 
  captionpos=b,                    
  keepspaces=true,                 
  numbers=left,                    
  numbersep=5pt,                  
  showspaces=false,                
  showstringspaces=false,
  showtabs=false,                  
  tabsize=2
}

\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}


\input{./tex/cBnotation.tex}


\begin{document}

	\begin{center}
		\textbf{\large Technical Assessment -- Carlo Brunetta}
		\vspace{2mm}
	\end{center}

	We expect you to send us within 7 days: a report answering the questions,
	the list of tools you have used, code you may have developed.
	Please send us your results in a zip file, along with your report in readable format (e.g. pdf)
	Don't hesitate to also include things that did not work, as experimentation is an important
	part of science!
	%
	A Proof of Sequential Work (\PoSW) enables showing that some computation was going on for $T$ time
	steps since some statement was received.
	A lattice-based construction of \PoSW\ is given in \cite{EPRINT:LaiMal24}.

	\begin{enumerate}
		\item Present in a high-level way the construction given in \cite{EPRINT:LaiMal24}.
			Explain the intuition behind it.
		\item Fully specify the resulting protocol and prototype it with your favourite programming
			language/tool (e.g., Python, Sage, C++, Rust, ...).
		\item Analyse the efficiency of the implementation in terms of memory, communication and
			computation requirements.
		\item How to turn the above protocol into a non-interactive proof system? Write down the resulting
			system by fully specifying the different steps.
		\item Present one or two applications of the previous protocol and/or system.
	\end{enumerate}

	\vspace*{-10pt}
	\vfill
	
	\paragraph{Report Organisation.}
	\begin{itemize}
		\item \texttt{tex/} Folder containing all the \TeX\ files to generate the report.
		\item \texttt{code/} Folder containing the implemented code.
		\begin{itemize}
			\item \texttt{code/main.py} Main script to run the \PoSW\ prototype.
			\item \texttt{code/posw.py} \PoSW\ implementation.
			\item \texttt{code/ring.py} Ring and related functionalities implementation.
			\item \texttt{code/debug.py} Unpolished testing/debugging script.
		\end{itemize}
		\item \texttt{report.pdf} This file: the report as a PDF with table of contents:
			\renewcommand\contentsname{\vspace*{-35pt}}
			\setcounter{tocdepth}{1}
			\tableofcontents
	\end{itemize}

	\mindnote{
		I will add in grey-coloured boxes (like this one) personal notes, failed attempts or similar.\\
		Anything that I would share with others when brainstorming/solving problems!
	}

	\vfill
	
	\paragraph{List of Tools.}
	The report is written in \LaTeX\ using an (evolving) personal template for quick notes and
	\msf{Grammarly} always checking for typos.
	The bibliography is a mix of \msf{cryptobib} and \msf{eprint}'s \BibTeX\ entries.
	%
	The code was first designed on pen-and-paper and later developed in \msf{Python}.
	Some tedious coding parts (e.g. command-line interface and comments/structuring) are
	modified versions of generated code from \msf{ChatGPT}, i.e. first generate the skeleton-code
	and later fill up with my comments/algorithms.

	The construction correctness, analysis and other examples are all developed on pen-and-paper.

	\vspace{1mm}
	\mindnote{I might have misunderstood the meaning of the request. Sorry if this is the case! }
	
	\vfill


	\clearpage
	\input{tex/explanation}
	\input{tex/prototype}
	\clearpage
	\input{tex/analysis}
	% \clearpage
	\input{tex/noninteractive}
	\input{tex/applications}

	% \clearpage
	\bibliographystyle{alphaurl}
	\bibliography{abbrev3,biblio}


\end{document} 
