% !TeX root = ../report.tex

\section{Tools and }\label{sec:applications}

\begin{center}
	\itshape The list of tools you have used
\end{center}

As pointed out by the authors, the \PoSW\ primitive is one of many primitives in the
timed cryptography domain which has some well-established applications classes.
The applications that fully utilise the \PoSW\ primitive are presented.

\vspace{2mm}
\mindnote{
	If $T$ implies a delay $\Delta$, effectively there are other interesting application which
	not necessarily requires the verification step except if one wants to fast-forward between
	sequential evaluations.
	The applications are based on time-lock puzzles.
	For example time-capsules and the ``encrypting for the future'' idea~\cite{EC:BDDNO21})
	or turn-based consistent communication channel~\cite{PROVSEC:BLLMT21} (a-la blockchain).

	The ``issue''	is that $\Delta$ time must be invested making it realistically prohibitive
	to design complex feature around these ideas.
	The alternative would be to have a trapdoor to quickly obtain $\vy$ which goes against
	the \PoSW\ definition.
	That is why I avoided presenting them too much.
}



\paragraph{Lotteries and MPC Fairness.}
	Guaranteeing randomness to the randomly sampled is hard and important.
	The main concern is that the random oracle is an ideal object while the hash/PRF are the closest
	objects that we commonly agree to look/be pseudo-random.
	When considering multi-party settings, it is of vital importance that any pseudo-random evaluation
	to be verifiable to avoid a malicious actor to influence the output to his/her favour.
	
	If computing $\PoSW$ on some large $T$ has controlled computationally cost/timing $\Delta$
	(one can somehow fix $T$ to identify a computational timing $\Delta$), then the primitive can be
	used to run anything in the lottery class:
	a conductor sets up a lottery where people can register before a pre-decided registration deadline.
	When the deadline is over, the conductor must honestly sample a winner uniformly at random from the
	registered people which can verify that the sampling was done correctly.
	
	This can be done by letting the conductor to set up a \PoSW, collect all the registration and use
	such information as the input $x$ for the $\PoSW$.
	Because of the primitive sequentiality and the full input being only effectively available only
	at the deadline,
	if $T$ is big enough to create an appropriate delay $\Delta$, the final winner is unknown to
	everyone (conductor comprised) making the lottery fair.
	Plus, the conductor must provide a proof $\pi$ which people can use to verify the correct winner's
	sampling.

	The class of lotteries contains many applications where the goal is to select an unpredictable
	candidate from a list.
	For example, one can use them for other type of consensus protocols, emulating the creation
	of a common-reference-string, sampling randomness in multi-party computations.
	


\paragraph{Expiring Password/Secrets}
	
	This application wants to force a prover to expire a password/secret.
	Consider a secret $\vx$ with a liveliness-budget of $T$.
	The verifier, starting from a shared value $\vy[T]$ and $T$, requires the prover to slowly
	consume its budget by an amount $t_i \leq T$ until $\vx$ is revealed.
	
	This is easy to achieve if the prover creates the challenge and never releases $\vx$.
	When the verifier request to verify and consume $t_1$, the prover provides the proof
	of correct $t_1$ evaluation from $\vy[T-t_1]$ until $\vy[T]$.
	The next request on $t_2$ provides the proof from $\vy[T-t_1-t_2]$ until $\vy[T-t_1]$ and so on.
	When $\sum t_i > T$, the prover should not be able to provide a proof forcing the prover to
	output $\vx$ which expires the secret.
	
	This idea is similar to a multi-stage commitment scheme where the commitments are chained and
	opened in sequence.
	The effective gain is that there is an additional possibility to quickly open $t_i$ stages
	with a reduced cost of $\log(t_i)$ for verifying the commitment.
	
	A possible application can use the secrets $\vy[i]$ for $i\in[0,T]$ which automatically gets
	revealed when the budget is consumed.
